\begin{fullwidth}
    \chapter*{Liste de publications}\label{ch-liste-publis}
    \addcontentsline{toc}{chapter}{Liste de publications}
    \markboth{Liste de publications}{}
    
    \subsection*{Journaux internationaux}
    
    % \begin{thebibliography}{xxxx}

        \bibitem[Monier~2018]{monier2018tci}
        E.~Monier, T. Oberlin, N.~Brun, M.~Tenc\'e, M.~de~Frutos et N.~Dobigeon.
        \newblock {\em Reconstruction of partially sampled multi-band images --
          {A}pplication to {EELS} microscopy}.
        \newblock IEEE Trans. Comput. Imag., vol.~4, no.~4, pages 585--598, Dec. 2018.

        \bibitem[Monier~2020]{Monier_Ultramicroscopy_2020}
        E.~Monier, T. Oberlin, N.~Brun, X.~Li, M.~Tenc\'e et N.~Dobigeon.
        \newblock {\em Fast reconstruction of atomic-scale {STEM-EELS} images from
          sparse sampling}.
        \newblock Ultramicroscopy, 2020.

    % \end{thebibliography}

    \subsection*{Conférences internationales}
    
    % \begin{thebibliography}{xxxx}

        \bibitem[Monier~2017a]{monier2017icassp}
        E~Monier et G~Chardon.
        \newblock {\em Cram{\'e}r-Rao bounds for the localization of anisotropic
          sources}.
        \newblock In Proc. IEEE Int. Conf. Acoust., Speech and Signal Process.
          (ICASSP), pages 3281--3285, 2017.

        \bibitem[Monier~2017b]{monier2017mm}
        E.~Monier, T. Oberlin, N.~Brun, M.~Tenc\'e et N.~Dobigeon.
        \newblock {\em Reconstruction of randomly and partially sampled {STEM}
          spectrum-images}.
        \newblock In Microsc. Microanal., volume~23, pages 170--171, Saint Louis, USA,
          Aug. 2017.

        \bibitem[Monier~2018a]{monier2018whispers}
        E.~Monier, T. Oberlin, N.~Brun, M.~de~Frutos, M.~Tenc\'e et N.~Dobigeon.
        \newblock {\em Reconstruction of partially sampled {EELS} images}.
        \newblock In Proc. IEEE GRSS Workshop Hyperspectral Image SIgnal Process.:
          Evolution in Remote Sens. (WHISPERS), Amsterdam, Netherlands, Sept. 2018.

        \bibitem[Monier~2018b]{monier2018jeels}
        E.~Monier, T. Oberlin, N.~Brun et N.~Dobigeon.
        \newblock {\em A Partial Random Sampling {STEM} Procedure For Sensitive
          Samples}.
        \newblock In Proc. JEELS conference, Porquerolles, France, June 2018.

        \bibitem[Monier~2019]{monier2019spars}
        E.~Monier, T. Oberlin, N.~Brun et N.~Dobigeon.
        \newblock {\em Reconstruction of partially sampled {STEM-EELS} images with
          atomic resolution}.
        \newblock In Proc. Workshop Signal Process. with Adaptative Sparse Structured
          Representations (SPARS), Toulouse, France, July 2019.

    % \end{thebibliography}
    
    \subsection*{Conférences nationales}  
    
    % \begin{thebibliography}{xxxx}

        \bibitem[Monier~2017]{monier2017gretsi}
        E.~Monier, T. Oberlin, N.~Brun et N.~Dobigeon.
        \newblock {\em Reconstruction de spectres-images partiellement
          \'echantillonn\'es en microscopie {EELS}}.
        \newblock In Actes du Colloque GRETSI, Juan-les-Pins, France, 2017.

        \bibitem[Monier~2019]{monier2019sfmu}
        E.~Monier, T. Oberlin, N.~Brun, M.~Tenc\'e, M.~de~Frutos et N.~Dobigeon.
        \newblock {\em Reconstruction de spectres-images STEM-EELS partiellement
          \'echantillonn\'es}.
        \newblock pages 74--75, July 2019.

    % \end{thebibliography}

    
    \subsection*{Rapports techniques}

    % \begin{thebibliography}{xxxx}

        \bibitem[Monier~2020]{Monier_TechReport_2020}
        E.~Monier, T. Oberlin, N.~Brun, M.~Tenc\'e, X.~Li et N.~Dobigeon.
        \newblock {\em Fast reconstruction of atomic-scale {STEM-EELS} images from
          sparse sampling -- {C}omplementary results}.
        \newblock Rapport technique, University of Toulouse, IRIT/INP-ENSEEIHT, France,
          Feb. 2020.

    % \end{thebibliography}



\end{fullwidth}